---
title: "Peer_Review_Mudith Ekanayake"
author: "Giang Nguyen"
date: "3/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ## Data Processing
snp_data <- snp_data[c(1,3,4,2,5:15)] # I think we need information from column 1,3, and 4. Why you also access 2, and 5:15?

Why dont you try laaply and sapply functions?
 to avoid loop?

For example:


maize_ded <- data.frame(lapply(maize_genotypes, as.character), stringsAsFactors=FALSE)
 #To created another data frame for maize_genotype, I used lapply function to return a list of maize_genotype, each element of which is the result of applying as.character function to the corresponding element of maize genotype. 

maize_ded <- data.frame(sapply( maize_ded,function(x) { x <- gsub("?","-",x,fixed=TRUE)} ))
  # then I used gsub function to search for "?" and "-" in maize_ded, but sapply returns a vector or matrix.

I think you also can try gsub() function for searching.

 
### Plotting

I was not able to access your graph. 



```{r cars}

```


